---
title: "Times"
subtitle: "A Reproducible Guide to Measure and Quantify Time Estimates of Projects"
author: "Zachary Palmore"
date: "5/23/2022"
output: 
   rmdformats::readthedown:
    highlight: kate
    toc_depth: 3
    code_folding: "hide"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<hr/>

<i>This report was started prior to any mention of a presentation of my times or use of my time management system for our performance management system</i>

<hr/>

```{r packages}

```

## Summary

The average time spent on projects was `r` [units].

## Background

As of this writing there are three methods in-use for tracking employee time including one designed for HR, another for internal use called the In-Out Health Board, and one for Rock County Public Health Department (RCPHD) Grant Tracking and Billing known as Dailies. A new employee ID-based method is also being considered by county officials but has not yet been deployed. There are benefits and drawbacks to each of these methods, however, their end goals are the same. They each want to know how much time is being spent in an area. Where they differ is in their specific area's of interest.

### HR Method

#### Overview

The traditional accounting process for our team is the human resources (HR) method. In this method every individual employee edits and emails an excel spreadsheet that the individual fills out for themselves based on a template provided by HR. They do this so that the accounting department in HR knows what to pay the employee. Individuals repeat this process each pay period. These excel spreadsheets are also known as employee time sheets. These are sent to an in-house RCPHD accountant who validates the times entered with the employee's supervisor. If the supervisor, accountant, and employee are in agreement then the in-house accountant sends it to the accountants in HR.

These spreadsheets are eventually delivered to an HR accounting group who has specific interests in what they track and must follow applicable rules and statutes. They want to know when the individual took a lunch, when the individual came back from lunch, when they started and ended their day, whether any sick or leave time was used, if it was a holiday, and other figures because they are required to report those statistics. This method requires that the individual calculate using excel or other general estimation before entering in their hours and times. The fields within the template spreadsheet are present due to rules and regulations. For these reasons, they are also limited in the insights they can produce.

#### Limitations

The main limitations that stem from the enforcement of these rules and regulations in the HR method come from the validity, reporting, and collection of the data. Validity refers to how truthful the data is and can be observed by measuring how closely the data collected from the individuals matches reality of how the individual's spend their time. Reporting concerns stem from the manner in which the data are presented. These could be observed through bias assessments and other evaluations of the sources when presenting finalized, approved information to decision makers, which are often subjectively delivered to adhere to politically motivated actions and statutes. Lastly, the limitation of the collection of the data refers to the process by which the data came to exist. It contains the steps involved from written rules and statute to submission of approved spreadsheets for payment of the employee.

Invalid and untruthful times are entered into spreadsheets because employees are required to report times in 15-minute intervals, make sound judgement regarding what categories to enter their time into, and perform their own calculations with little to no training on how this should be done. Employees who are not documenting each interval of time correctly may face consequences for violations. There are safeguards in place in the event that the individual miscalculates or fails to categorize correctly. Usually, this is corrected by the in-house accountant or supervisor prior to submission to the HR accountants. However, the safeguards do not solve the root cause of this limitation.

Asking for employees to be this precise with their time entries when few individuals track their time in such specific intervals introduces new sources of error and discourages employees to be truthful. Employees, who are motivated by their pay, would like to have as much pay as possible for the least amount of time. Any barrier created to prevent the person's ability to earn more should be carefully thought through before being implemented to reduce its impact on productivity and employee self-worth as much as possible.

During interviews and conversations before hire it is typical to hear the word "salaried" when discussing the individual's pay, however, this is a false assumption. By definition the term salaried is reserved for an individual employee that gets paid the same amount each week regardless of how many hours they worked. It is fixed income without the need for hourly justification. If this were the case, no salaried employee would need to worry about tracking their hours properly. Yet, this is exactly what this method attempts to do. This causes confusion among the individuals involved in the collection and review process for both salaried and non-salaried employees.

The idea that an employee can be both salaried and paid by the hour is incompatible with their definitions and causes disagreement for the employees who are entering their time. For the employee who thinks themselves salaried, the workload of time tracking is superfluous. For the employee who thinks themselves waged, they are discouraged from working until their rate is increased upon acquiring overtime.

Approval for any work over the set schedule is also required meaning, if you do work over the allotted hours expected in a week, you may not be compensated without prior approval. This effects how time is entered. To circumvent this, employees track times in a set schedule, for example, 9-5, on a regular basis with minimal deviation due to the multitude of conflicting pressures. These pressures create a weighted ceiling effect, in which the amount an individual can make is capped and hard to lift. This portion of the method contributes to reporting and collection issues but is especially validity issues.

Validity is reduced further by these requirements shrinking the total time paid for the employee to only the intervals in which work is being done. This implies no value is generated outside of those immediate intervals. The idea is great for business interests, where the goal is to be as productive as possible with the least amount of money, but it lacks personnel interests. Personnel, when not strictly managed by someone with keen motivations to achieve business interests, then deviate from the business interests to promote their own wealth and well being. This competition at scale opens new opportunities for exploitation for both business and personnel, discouraging both from being truthful.

Workplace culture also influences this method negatively by forcing all employees to follow a rigid structure that may not function for them. Consider for a moment, when an individual starts in a new role, what category does the time for orientation get placed under? How about the time driving to and from orientation if it is at a separate building and is it paid? There may be safeguards in place with written expectations for common abnormalities to address these concerns. However, are there contingencies in places for all possible cases? Unless this method had a near perfect documentation that everyone understood and used to make sound judgments when entering their times, the premise for its collection is heavily biased towards business interests.

Reduced objectivity, limited opportunity for questions, and the business leaning bias leads to misinformation and poorer decision-making than simply having an employee track their time for their own analysis with no consequences. It is because of workplace culture that only a small subset of the working population second guesses how this data is entered or handled. This contributes to the improper reporting of this information where individuals who are immersed in this workplace culture are pressured to contribute to its business interests.

A culmination of negative workplace culture influences, outdated policies, slow to change business focused employee subjectivity, and individual employee requirements have led to a poor data collection process. As it exists, this system encourages employees to submit the same time sheets repeatedly with only name and data changes regardless of its validity. Deviations from normal schedules are cause for concern or questioning. To avoid conflict and get paid the salary promised, the individual submits and moves forward. How the data is collected is just as important if not more important than the resulting statistics and the HR method gives little to no consideration for this beyond legal obligations.

For these reasons the HR method is not an accurate representation of reality and could benefit from a reevaluation of its validity, reporting, and data collection process. Aside from the aforementioned limitations this process is also quite laborious requiring entire teams of people to pay a single person. Hardly any of these teams focus on finding truthfulness because doing so is a lot of work in this system. Policies dictate what gets tracked and have produced a rigid system built mainly on historical factory schedules when we have economically grown into new sectors of service that no longer fit those schedules nor does the workplace function like an assembly line. We do not produce products. We provide services now. Therefore, how this time gets tracked should change to reflect the current workplace and new options should be explored that make it less laborious for an already hyper productive workforce.

### In-Out Board

#### Overview

Within the virtual environment of a Citrix based virtual network an application was developed to track the presence or absence of health staff. This was named the "In-Out Health Board." This section describes the process of the In-Out Health Board method, hereafter known as the IOHB.

The IOHB has a spreadsheet user interface originally designed to make it easier for personnel to determine whether another person is in the office or not. Upon switching to work-from-home and remote offices employees were asked to track when they check-in and check-out using this board through the Citrix platform. The board was also intended to be used to denote if an individual was out to lunch, working in the field, and provided some conditional formatting and coloration to assist the reader.

This system is only available to those with administrative privileges and permission is granted by an IT professional of Rock County. It is meant to function as a time clock where an individual, upon arrival to the office or logging in at home, would open the application and set their status to 'working' with a check-in time entry. Upon leaving for lunch or at the end of their day, the same individual would then check-out with another corresponding time entry beside their name. By this mechanism for check-in and check-out, one could also use this system for informing some of the existing HR method's time sheets but the systems themselves are separate.

#### Limitations

The limitations of the In-Out Health Board (IOHB) come mainly in two forms: usage and validity. Usage refers to the total number of users of the system. It is measured by counting the number of users entering their times into the system (active users) and adding to that the number of individuals watching the system (passive users). Validity is how well the data depicts reality and it can be measured by observing how closely the data collected from the active users matches reality of how the same active users spend their time.

Less than a quarter of the 43 staff employed by RCPHD were estimated to use the system when in the office and those who use it the most frequently often forget to track their time appropriately. Having fewer active users than the system was designed for reduces its ability to provide insights. It is estimated that the number of passive users is approximately 10-11 staff when in the office. These individuals are also the same staff who access the board recurrently.

The insights gained from this small subset of the workplace may be unintentionally misinforming passive users of the system by presenting times that are not being properly tabulated from active users who are only partially managing there time through this system. This is a major limitation, especially if it is used to inform any individual who does not have knowledge of these limitations.

The system was developed by someone outside of RCPHD to support time tracking capabilities within the department and give support staff, nurses, and environmental health professionals an easy indicator of presence or absence of an employee at a given time. However, for those who are using it, they tend to check-in but fail to check-out. Support staff sometimes will fix this and mark an individual out if they notice someone is remote or not in the office. Fixing the board requires that the support staff already be aware of whether an individual is present or absent in the office. This defeats the purpose of the board and renders it useless in these cases.

Outside of the office, usage drops to near zero. When at home no individual has spoke positively about using the Citrix platform and office culture has successfully phased out its use. Anyone who claims to have used it at one point complains that it is too slow and that they no longer use it anymore because of how slow it is. By this evidence alone, the possibility of the IOHB method being effectively used is highly unlikely.

### Dailies Method

#### Overview

The webpage titled RCPHD Billing, otherwise known as Dailies, is an active server page (aspx) file developed by Rock County IT Department and and hosted on the network 'rocky.' Its creator and maintainer is thought to be Linda Updike who is said to still manage the information that flows through the system. The purpose of this system is to track how much time each individual spends working on projects and analyze the time spent by project area. In an ideal situation, the insights gained from the organizing and summing of data by billable categories would allow for the proper billing of grants.

There are 10 fields for tracking work performed including: the individual's name, the date, number of hours spent, miles traveled, travel hours, a check box to denote if travel occurred in a county vehicle, what program the individual performed the work in, the sub-program, activity category, cost center. The required fields are the name, date, hours spent, travel miles and hours, program and sub-program. If there was no travel for the project, the individual would enter a zero. The program tracks the working group the individual is performing work in while the sub-program tracks the billable categories relevant to that work. For example, in the Public Health Preparedness & Response (PHEP) program there are two sub-programs: COVID-19 General and PHEP General. The individual selects the sub-program specific to their work. The Activity and Cost Center fields are not required. Once completed the individual clicks an "Add" button which tabulates the total hours worked by week and day. These can be reviewed with user-specified dates from the webpage as well by clicking on the "Review" button.

Individuals are asked by management to enter their time into this system to track all the work they do since it is quite difficult to distinguish grant-work from regular public health work. They are given a reference spreadsheet with short descriptions of each with a generalized sentence about when the program should be selected and who the primary users are of the sub-program. At regular intervals, management reviews the tabulated results to make budgeting decisions.

#### Limitations

The limitations of the Dailies method could be categorized into three groups: knowledge and skills gaps, usage, and validity. A knowledge and skills gap is difficult to measure exactly but could be estimated by surveying the population of users and seeing if how they interact with the system is different than how it should be interacted with. This might include measuring how far off the individuals are from the expected or intended categorization. Usage is a count of the total number of users making use of the system. It can be further subdivided into active and passive users. Active users can be defined as the number of users entering their times into the system while passive users are those who are watching the system. Lastly, validity is how well the data depicts reality. It could be measured by observing how closely the data collected from the active users matches the reality of how the active users are categorizing and spending their time on projects.

The knowledge and skills gap is clearest in the categorization of time into sub-projects, wherein no individual categorizes the same way. For example, two individuals who work on the same task will often have different categories to

### DS Method

There no methods for tracking data science projects or time at RCPHD.

Management is interested learning what the data scientist is doing, when, and gaining an overall better understanding of how much time the data scientist spends on various projects. At this time (6/14/2022) they are also interested in learning what projects the data scientist is choosing to work on (since no specifics have been given). It is also important that the process be automatic as much as possible.
