---
title: "Ph.D. Program Exploration"
format: html
editor: visual
---

```{r}
#| echo: false
#| warning: false
source("prep.r")
library(dplyr)
```

## Collection

This data was collected from [University of Wisconsin Program Guide](https://guide.wisc.edu/mas/) as of June 2023. There are `r length(unique(responses$Programs))` programs with ratings. Only those programs that I viewed as possible or worth considering were included. Each program was then rated by me either with someone else reading me the program names and entering a number on a scale 1-5 to indicate my interest level in pursing a Ph.D. in that program.

## Top Programs

```{r}
library(tidyr)
responses %>% 
  group_by(Program, Interest) %>% 
  reframe(count = n()) 
wide <- responses %>% 
  spread(Program, Interest) 
wide
  
```


```{r}
responses %>% 
  group_by(Program, Interest) %>% 
  reframe(n())

med_responses <- responses %>% 
  group_by(Program) %>%
  reframe(Median = median(as.numeric(Interest))) 
library(ggplot2)
med_responses %>%
  ggplot(aes(reorder(Program, Median), Median)) + 
  geom_col(aes(fill = Program)) + 
  theme(legend.position = "none")
```



```{r}
responses %>% 
  group_by(Interest) %>%
  reframe(count=n()) %>% 
  ggplot(aes(Interest, count)) + 
  geom_col()

responses %>% 
  group_by(DateTime, Interest) %>% 
  reframe(count = n()) %>% 
  ggplot(aes(Interest, count)) + 
  geom_col() + facet_wrap(~DateTime)

responses %>% 
  group_by(Program) %>% 
  reframe(Variance = var(as.numeric(Interest)),
          Mean = mean(as.numeric(Interest)),
          Median = median(as.numeric(Interest)), 
          Max = max(as.numeric(Interest)), 
          Min = min(as.numeric(Interest))) %>% 
  arrange(desc(Variance))

summary(responses$Interest)[[4]] + summary(responses$Interest)[[5]] 
responses$Interest)


levels(responses$Interest)[[5]]

```




