---
title: "Rock County Mortality"
author: "Z. Palmore"
date: "5/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## The Query 

We organize the endpoints of the query using the selector layout of Provisional Mortality Statistics provided by the CDC data request system. This begins with the table layout containing group-by 

This begins with the organization of the table layout itself using group by functions. 


# Warnings

All 2021 data is provisional - subject to change
All 2022 data is provisional and partial - subject to change and missing records from states

```{r}
# REG stands for Race, Ethnicity, Gender
REG2018 <- read.delim(file = "Data/ICD10_REG_2018.txt", header = T, sep = "\t", quote = "\"", 
           dec = ".", fill = T, comment.char = "")
REG2019 <- read.delim(file = "Data/ICD10_REG_2019.txt", header = T, sep = "\t", quote = "\"", 
           dec = ".", fill = T, comment.char = "")
REG2020 <- read.delim(file = "Data/ICD10_REG_2020.txt", header = T, sep = "\t", quote = "\"", 
           dec = ".", fill = T, comment.char = "")
REG2021 <- read.delim(file = "Data/ICD10_REG_2021.txt", header = T, sep = "\t", quote = "\"", 
           dec = ".", fill = T, comment.char = "")
REG2022 <- read.delim(file = "Data/ICD10_REG_2022.txt", header = T, sep = "\t", quote = "\"", 
           dec = ".", fill = T, comment.char = "")
ROCKREG2018 <- REG2018 %>% 
  filter(Occurrence.County == "Rock County, WI")
ROCKREG2019 <- REG2019 %>% 
  filter(Occurrence.County == "Rock County, WI")

rbind(ROCKREG2018, ROCKREG2019) # Need a Year attached to each from read-in

REG2018$Year <- as.numeric(2018)
REG2019$Year <- as.numeric(2019)
REG2020$Year <- as.numeric(2020)
REG2021$Year <- as.numeric(2021)
REG2022$Year <- as.numeric(2022)

reg <- rbind(REG2018, REG2019, REG2020, REG2021, REG2022) # Note that CDC data goes through March in 2022
```


Does not matter whether the 95% CI is checked nor any other box. It will either produce an error and request changes or spit out the data set as if the boxes were not checked.

"---"
"Dataset: Provisional Mortality Statistics, 2018 through Last Month"
"Query Parameters:"
"Occurrence States: Wisconsin (55)"
"Residence States: Wisconsin (55)"
"Year/Month: Jan., 2018"
"Group By: Occurrence County; UCD - ICD Chapter; Single Race 6; Hispanic Origin; Gender"
"Show Totals: Disabled"
"Show Zero Values: Disabled"
"Show Suppressed: False"
"Calculate Rates Per: 100,000"
"Rate Options: Default intercensal populations for years 2001-2009 (except Infant Age Groups)"
"---"
"Help: See http://wonder.cdc.gov/wonder/help/mcd-provisional.html for more information."
"---"
"Query Date: May 4, 2022 10:32:28 AM"
"---"
"Suggested Citation: Centers for Disease Control and Prevention, National Center for Health Statistics. Provisional Multiple"
"Cause of Death on CDC WONDER Online Database. Data are from the final Multiple Cause of Death Files, 2018-2020, and from"
"provisional data for years 2021-2022, as compiled from data provided by the 57 vital statistics jurisdictions through the Vital"
"Statistics Cooperative Program. Accessed at http://wonder.cdc.gov/mcd-icd10-provisional.html on May 4, 2022 10:32:28 AM"
"---"




```{r}
# Data need cleaning before read-in? Yes. Last 64 rows contain notes in every instance. 
REG2018_JAN <- read.delim(file = "Data/REG_2018_JAN.txt", header = T, sep = "\t", quote = "\"", 
           dec = ".", fill = T, comment.char = "")
tail(REG2018_JAN, 65)
REG2018_APR <- read.delim(file = "Data/REG_2018_APR.txt", header = T, sep = "\t", quote = "\"", 
           dec = ".", fill = T, comment.char = "")
tail(REG2018_APR, 65)
REG2019_APR <- read.delim(file = "Data/REG_2019_APR.txt", header = T, sep = "\t", quote = "\"", 
           dec = ".", fill = T, comment.char = "")
tail(REG2019_APR, 64)
head(REG2019_APR, -64)

head(read.delim(file = "Data/REG_2019_APR.txt", header = T, sep = "\t", quote = "\"", 
           dec = ".", fill = T, comment.char = ""), -64) %>% 
  mutate(Path = "Data/REG_2019_APR.txt")
?as.Date()
```




```{r}

dataFiles <- lapply(Sys.glob("REG_*.txt"), read.delim(., 
                    header = T, sep = "\t", quote = "\"", dec = ".", 
                    fill = T, comment.char = ""))

files <- lapply(Sys.glob("REG_*.txt"), read.delim)
Sys.glob("Data/*.txt")
dataFiles <- lapply(Sys.glob("Data/REG_*.txt"), read.delim)

paths <- Sys.glob("Data/REG_*.txt")

ldf <- list()
for (k in 1:length(paths)){
 ldf[[k]] <- read.delim(paths[k])
}

for (k in 1:length(paths)){
 ldf[[k]] <- head(read.delim(file = paths[k], header = T, sep = "\t", quote = "\"", 
           dec = ".", fill = T, comment.char = ""), -64) %>% 
   mutate(Path = paths[k])
}

library(stringr)
str_extract_all(paths, pattern = "_\\d{4}_")
paths$year <- str_extract_all(paths, pattern = "\\d{4}")
str_extract_all(paths, pattern = "REG_")
str_extract_all()

class(paths)

for (i in 1:length(ldf)){
  
}


Sys.glob("Data/REG_*.txt")

list.files()

```



```{r}
months <- c("JAN", "FEB", "MAR", "APR", "MAY", "JUN", "JUL", "AUG", "SEP", 
     "OCT", "NOV", "DEC")
for (k in 1:length(months)){
 df <- head(read.delim(file = months[k], header = T, sep = "\t", quote = "\"", 
           dec = ".", fill = T, comment.char = ""), -64) %>% 
   mutate(Path = month[k])
}


paths_2018 <- ""

for (i in 1:length(months)){
  paths_2018[[i]] <- paste0("Data/2018/REG_2018_", months[i], ".txt")
}
ldf <- ""
for (i in 1:length(paths_2018)){
 ldf[[i]] <- head(read.delim(file = paths_2018[i], header = T, sep = "\t", quote = "\"", 
           dec = ".", fill = T, comment.char = ""), -64) %>% 
   mutate(Path = paths_2018[i])
}

paths_2018

```



```{r}
REG_2018_JAN <- head(read.delim(file = "Data/2018/REG_2018_JAN.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2018, 
         Month = "JAN", 
         Date = as.Date("2018-01-01"))

REG_2018_FEB <- head(read.delim(file = "Data/2018/REG_2018_FEB.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2018, 
         Month = "FEB", 
         Date = as.Date("2018-02-01"))

REG_2018_MAR <- head(read.delim(file = "Data/2018/REG_2018_MAR.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2018, 
         Month = "MAR", 
         Date = as.Date("2018-03-01"))

REG_2018_APR <- head(read.delim(file = "Data/2018/REG_2018_APR.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2018, 
         Month = "APR", 
         Date = as.Date("2018-04-01"))

REG_2018_MAY <- head(read.delim(file = "Data/2018/REG_2018_MAY.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2018, 
         Month = "MAY", 
         Date = as.Date("2018-05-01"))

REG_2018_JUN <- head(read.delim(file = "Data/2018/REG_2018_JUN.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2018, 
         Month = "JUN", 
         Date = as.Date("2018-06-01"))

REG_2018_JUL <- head(read.delim(file = "Data/2018/REG_2018_JUL.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2018, 
         Month = "JUL", 
         Date = as.Date("2018-07-01"))

REG_2018_AUG <- head(read.delim(file = "Data/2018/REG_2018_AUG.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2018, 
         Month = "AUG", 
         Date = as.Date("2018-08-01"))

REG_2018_SEP <- head(read.delim(file = "Data/2018/REG_2018_SEP.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2018, 
         Month = "SEP", 
         Date = as.Date("2018-09-01"))

REG_2018_OCT <- head(read.delim(file = "Data/2018/REG_2018_OCT.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2018, 
         Month = "OCT", 
         Date = as.Date("2018-10-01"))

REG_2018_NOV <- head(read.delim(file = "Data/2018/REG_2018_NOV.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2018, 
         Month = "NOV", 
         Date = as.Date("2018-11-01"))

REG_2018_DEC <- head(read.delim(file = "Data/2018/REG_2018_DEC.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2018, 
         Month = "DEC", 
         Date = as.Date("2018-12-01"))

REG_2018_MONTHS <- 
  rbind(REG_2018_JAN, REG_2018_FEB, REG_2018_MAR, REG_2018_APR, REG_2018_MAY, REG_2018_JUN,
      REG_2018_JUL, REG_2018_AUG, REG_2018_SEP, REG_2018_OCT, REG_2018_NOV, REG_2018_DEC)
```




```{r}
REG_2019_JAN <- head(read.delim(file = "Data/2019/REG_2019_JAN.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2019, 
         Month = "JAN", 
         Date = as.Date("2019-01-01"))

REG_2019_FEB <- head(read.delim(file = "Data/2019/REG_2019_FEB.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2019, 
         Month = "FEB", 
         Date = as.Date("2019-02-01"))

REG_2019_MAR <- head(read.delim(file = "Data/2019/REG_2019_MAR.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2019, 
         Month = "MAR", 
         Date = as.Date("2019-03-01"))

REG_2019_APR <- head(read.delim(file = "Data/2019/REG_2019_APR.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2019, 
         Month = "APR", 
         Date = as.Date("2019-04-01"))

REG_2019_MAY <- head(read.delim(file = "Data/2019/REG_2019_MAY.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2019, 
         Month = "MAY", 
         Date = as.Date("2019-05-01"))

REG_2019_JUN <- head(read.delim(file = "Data/2019/REG_2019_JUN.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2019, 
         Month = "JUN", 
         Date = as.Date("2019-06-01"))

REG_2019_JUL <- head(read.delim(file = "Data/2019/REG_2019_JUL.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2019, 
         Month = "JUL", 
         Date = as.Date("2019-07-01"))

REG_2019_AUG <- head(read.delim(file = "Data/2019/REG_2019_AUG.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2019, 
         Month = "AUG", 
         Date = as.Date("2019-08-01"))

REG_2019_SEP <- head(read.delim(file = "Data/2019/REG_2019_SEP.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2019, 
         Month = "SEP", 
         Date = as.Date("2019-09-01"))

REG_2019_OCT <- head(read.delim(file = "Data/2019/REG_2019_OCT.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2019, 
         Month = "OCT", 
         Date = as.Date("2019-10-01"))

REG_2019_NOV <- head(read.delim(file = "Data/2019/REG_2019_NOV.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2019, 
         Month = "NOV", 
         Date = as.Date("2019-11-01"))

REG_2019_DEC <- head(read.delim(file = "Data/2019/REG_2019_DEC.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2019, 
         Month = "DEC", 
         Date = as.Date("2019-12-01"))

REG_2019_MONTHS <- 
  rbind(REG_2019_JAN, REG_2019_FEB, REG_2019_MAR, REG_2019_APR, REG_2019_MAY, REG_2019_JUN,
      REG_2019_JUL, REG_2019_AUG, REG_2019_SEP, REG_2019_OCT, REG_2019_NOV, REG_2019_DEC)
```


```{r}
REG_2020_JAN <- head(read.delim(file = "Data/2020/REG_2020_JAN.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2020, 
         Month = "JAN", 
         Date = as.Date("2020-01-01"))

REG_2020_FEB <- head(read.delim(file = "Data/2020/REG_2020_FEB.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2020, 
         Month = "FEB", 
         Date = as.Date("2020-02-01"))

REG_2020_MAR <- head(read.delim(file = "Data/2020/REG_2020_MAR.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2020, 
         Month = "MAR", 
         Date = as.Date("2020-03-01"))

REG_2020_APR <- head(read.delim(file = "Data/2020/REG_2020_APR.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2020, 
         Month = "APR", 
         Date = as.Date("2020-04-01"))

REG_2020_MAY <- head(read.delim(file = "Data/2020/REG_2020_MAY.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2020, 
         Month = "MAY", 
         Date = as.Date("2020-05-01"))

REG_2020_JUN <- head(read.delim(file = "Data/2020/REG_2020_JUN.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2020, 
         Month = "JUN", 
         Date = as.Date("2020-06-01"))

REG_2020_JUL <- head(read.delim(file = "Data/2020/REG_2020_JUL.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2020, 
         Month = "JUL", 
         Date = as.Date("2020-07-01"))

REG_2020_AUG <- head(read.delim(file = "Data/2020/REG_2020_AUG.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2020, 
         Month = "AUG", 
         Date = as.Date("2020-08-01"))

REG_2020_SEP <- head(read.delim(file = "Data/2020/REG_2020_SEP.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2020, 
         Month = "SEP", 
         Date = as.Date("2020-09-01"))

REG_2020_OCT <- head(read.delim(file = "Data/2020/REG_2020_OCT.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2020, 
         Month = "OCT", 
         Date = as.Date("2020-10-01"))

REG_2020_NOV <- head(read.delim(file = "Data/2020/REG_2020_NOV.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2020, 
         Month = "NOV", 
         Date = as.Date("2020-11-01"))

REG_2020_DEC <- head(read.delim(file = "Data/2020/REG_2020_DEC.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2020, 
         Month = "DEC", 
         Date = as.Date("2020-12-01"))

REG_2020_MONTHS <- 
  rbind(REG_2020_JAN, REG_2020_FEB, REG_2020_MAR, REG_2020_APR, REG_2020_MAY, REG_2020_JUN,
      REG_2020_JUL, REG_2020_AUG, REG_2020_SEP, REG_2020_OCT, REG_2020_NOV, REG_2020_DEC)
```


```{r}
REG_2021_JAN <- head(read.delim(file = "Data/2021/REG_2021_JAN.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2021, 
         Month = "JAN", 
         Date = as.Date("2021-01-01"))

REG_2021_FEB <- head(read.delim(file = "Data/2021/REG_2021_FEB.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2021, 
         Month = "FEB", 
         Date = as.Date("2021-02-01"))

REG_2021_MAR <- head(read.delim(file = "Data/2021/REG_2021_MAR.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2021, 
         Month = "MAR", 
         Date = as.Date("2021-03-01"))

REG_2021_APR <- head(read.delim(file = "Data/2021/REG_2021_APR.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2021, 
         Month = "APR", 
         Date = as.Date("2021-04-01"))

REG_2021_MAY <- head(read.delim(file = "Data/2021/REG_2021_MAY.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2021, 
         Month = "MAY", 
         Date = as.Date("2021-05-01"))

REG_2021_JUN <- head(read.delim(file = "Data/2021/REG_2021_JUN.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2021, 
         Month = "JUN", 
         Date = as.Date("2021-06-01"))

REG_2021_JUL <- head(read.delim(file = "Data/2021/REG_2021_JUL.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2021, 
         Month = "JUL", 
         Date = as.Date("2021-07-01"))

REG_2021_AUG <- head(read.delim(file = "Data/2021/REG_2021_AUG.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2021, 
         Month = "AUG", 
         Date = as.Date("2021-08-01"))

REG_2021_SEP <- head(read.delim(file = "Data/2021/REG_2021_SEP.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2021, 
         Month = "SEP", 
         Date = as.Date("2021-09-01"))

REG_2021_OCT <- head(read.delim(file = "Data/2021/REG_2021_OCT.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2021, 
         Month = "OCT", 
         Date = as.Date("2021-10-01"))

REG_2021_NOV <- head(read.delim(file = "Data/2021/REG_2021_NOV.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2021, 
         Month = "NOV", 
         Date = as.Date("2021-11-01"))

REG_2021_DEC <- head(read.delim(file = "Data/2021/REG_2021_DEC.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2021, 
         Month = "DEC", 
         Date = as.Date("2021-12-01"))

REG_2021_MONTHS <- 
  rbind(REG_2021_JAN, REG_2021_FEB, REG_2021_MAR, REG_2021_APR, REG_2021_MAY, REG_2021_JUN,
      REG_2021_JUL, REG_2021_AUG, REG_2021_SEP, REG_2021_OCT, REG_2021_NOV, REG_2021_DEC)
```


```{r}
REG_2022_JAN <- head(read.delim(file = "Data/2022/REG_2022_JAN.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2022, 
         Month = "JAN", 
         Date = as.Date("2022-01-01"))

REG_2022_FEB <- head(read.delim(file = "Data/2022/REG_2022_FEB.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2022, 
         Month = "FEB", 
         Date = as.Date("2022-02-01"))

REG_2022_MAR <- head(read.delim(file = "Data/2022/REG_2022_MAR.txt", header = T, sep = "\t", 
                                quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
  mutate(Year = 2022, 
         Month = "MAR", 
         Date = as.Date("2022-03-01"))
# 
# REG_2022_APR <- head(read.delim(file = "Data/2022/REG_2022_APR.txt", header = T, sep = "\t", 
#                                 quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
#   mutate(Year = 2022, 
#          Month = "APR", 
#          Date = as.Date("2022-04-01"))
# 
# REG_2022_MAY <- head(read.delim(file = "Data/2022/REG_2022_MAY.txt", header = T, sep = "\t", 
#                                 quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
#   mutate(Year = 2022, 
#          Month = "MAY", 
#          Date = as.Date("2022-05-01"))
# 
# REG_2022_JUN <- head(read.delim(file = "Data/2022/REG_2022_JUN.txt", header = T, sep = "\t", 
#                                 quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
#   mutate(Year = 2022, 
#          Month = "JUN", 
#          Date = as.Date("2022-06-01"))
# 
# REG_2022_JUL <- head(read.delim(file = "Data/2022/REG_2022_JUL.txt", header = T, sep = "\t", 
#                                 quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
#   mutate(Year = 2022, 
#          Month = "JUL", 
#          Date = as.Date("2022-07-01"))
# 
# REG_2022_AUG <- head(read.delim(file = "Data/2022/REG_2022_AUG.txt", header = T, sep = "\t", 
#                                 quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
#   mutate(Year = 2022, 
#          Month = "AUG", 
#          Date = as.Date("2022-08-01"))
# 
# REG_2022_SEP <- head(read.delim(file = "Data/2022/REG_2022_SEP.txt", header = T, sep = "\t", 
#                                 quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
#   mutate(Year = 2022, 
#          Month = "SEP", 
#          Date = as.Date("2022-09-01"))
# 
# REG_2022_OCT <- head(read.delim(file = "Data/2022/REG_2022_OCT.txt", header = T, sep = "\t", 
#                                 quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
#   mutate(Year = 2022, 
#          Month = "OCT", 
#          Date = as.Date("2022-10-01"))
# 
# REG_2022_NOV <- head(read.delim(file = "Data/2022/REG_2022_NOV.txt", header = T, sep = "\t", 
#                                 quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
#   mutate(Year = 2022, 
#          Month = "NOV", 
#          Date = as.Date("2022-11-01"))
# 
# REG_2022_DEC <- head(read.delim(file = "Data/2022/REG_2022_DEC.txt", header = T, sep = "\t", 
#                                 quote = "\"", dec = ".", fill = T, comment.char = ""), -64) %>%
#   mutate(Year = 2022, 
#          Month = "DEC", 
#          Date = as.Date("2022-12-01"))
# 
REG_2022_MONTHS <- 
  rbind(REG_2022_JAN, REG_2022_FEB, REG_2022_MAR#, REG_2022_APR, REG_2022_MAY, REG_2022_JUN, 
        # REG_2022_JUL, REG_2022_AUG, REG_2022_SEP, REG_2022_OCT, REG_2022_NOV, REG_2022_DEC
        )
```



```{r}
REG_MORT <- rbind(REG_2018_MONTHS, REG_2019_MONTHS, REG_2020_MONTHS, 
           REG_2021_MONTHS, REG_2022_MONTHS)
```


