---
title: "WonderReport"
author: "Z. Palmore"
date: "5/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Background 

[This might answer the questions; What data are you working with? Where did it come from? How was it collected? Why was it collected? Who did the collecting? Develop a working knowledge of the data so that a good procedure can come naturally] 




Objectives 

[Set clear objectives. Are there any questions you want to answer? If so, what are they? State them.] 

 Goals: 

- How long can we expect to live in Rock County? 
  - Do Males or Females live longer and by how much? 
  - Do white live longer than black, asian, etc... and by how much? 
- How many people died in Rock County
  - Is this similar to neighboring counties? 
  - Is this similar to all counties in Wisconsin? 
  - Did more black, asian, etc... people die than white? 
- What did the people in Rock County die from? 
  - Is this similar to neighboring counties? 
  - Is this similar to all counties in Wisconsin? 
  - Did more black, asian, etc... people die from any specific disease than white people?
    - If so, what disease caused greater death to black, white, asian population in Rock?
  - Did more females die of a specific disease, if so what disease and by how much?
  - Did more males die of a specific disease, if so what disease and by how much?
- What are the age-adjusted death rates for race-ethnicity-sex groups? (See CDC US Mortality Report)
  - What is an age-adjusted death rate? 
  - Are the age-adjusted death rates equal across racial, ethinic, and gender groups? 
    - If not, how do they differ? 
- Did age-specific death rates change from previous years for those aged 1 year and over? (See CDC US Mortality Report)
  - If so, how did they change? 
  - Are things improving or getting worse for white, black, asian, etc... and how much? 
  - Are things improving or getting worse for male/females and how much? 
- What are the death rates for the 10 leading causes of death? (See CDC US Mortality Report)
  - What are the 10 leading causes in Rock County? 
  - Are they improving or getting worse from previous years? 
  - How do they compare to the rest of Wisconsin? 
- What are the mortality rates for the 10 leading causes of infant death?
  - What are the 10 leading causes of infant death? 
  - Are they improving or getting worse from previous years? 
  - How do these rates for infants compare to the rest of Wisconsin? 


Hypothesis 

[Answer the prompt; given what we know about the data and having set clear objectives and questions we intend to elucidate upon, what do we expect the outcome of this project to be?] 

 

Collection 

[Here we investigate the process currently used to collect and enter the data into the spreadsheets] 

 

Exploration 

[Section for learning about the data, its validity, challenges, and how we might solve or improve it before analysis] 



Preparation 

[ Section for cleaning up the data and documenting our steps as well as providing an explanation of why. This should build on the findings of the exploration section] 

```{r}
load("Data/reg_mort.rdata")
# Source US Census Bureau and World Population Review
RockPop2018 <- 162874 
RockPop2019 <- 163354
RockPop2020 <- 163687
RockPop2021 <- 164314
RockPop2022 <- RockPop2021 + (RockPop2021 * 0.0029) # Uses Annual Growth Rate each year for last 3 years (2021, 2020, and 2019)
# Rate taken from World Population Review 
# https://worldpopulationreview.com/us-counties/wi/rock-county-population
library(dplyr)
REG_MORT$Year <- as.character(REG_MORT$Year)
REG_MORT <- REG_MORT %>% 
  mutate(Population = 
           case_when(endsWith(Year, '2018') ~RockPop2018, 
           endsWith(Year, '2019') ~RockPop2019,
           endsWith(Year, '2020') ~RockPop2020,
           endsWith(Year, '2021') ~RockPop2021, 
           endsWith(Year, '2022') ~RockPop2022)) 
  
reg_mort$Year <- as.character(reg_mort$Year)
reg_mort <- reg_mort %>% 
  mutate(Population = 
           case_when(endsWith(Year, '2018') ~RockPop2018, 
           endsWith(Year, '2019') ~RockPop2019,
           endsWith(Year, '2020') ~RockPop2020,
           endsWith(Year, '2021') ~RockPop2021, 
           endsWith(Year, '2022') ~RockPop2022))
```

 

Modeling and Analysis 

[ Conduct analysis as achieve the objective, assess any models developed, and document the process ] 

- How many people died in Rock County
  - Is this similar to neighboring counties? 
  - Is this similar to all counties in Wisconsin? 
  - Did more black, asian, etc... people die than white? 

```{r}
sum(REG_MORT$Deaths)
sum(reg_mort$Deaths)
sum(reg_mort$Deaths, na.rm = T)
REG_MORT %>% 
  group_by(Year, Occurrence.County) %>% 
  summarise(Total = sum(Deaths))
reg_mort %>% 
  group_by(Year, Occurrence.County) %>% 
  summarise(Total = sum(Deaths, na.rm = T))
reg_mort %>% 
  group_by(Year) %>% 
  summarise(Total = sum(Deaths, na.rm = T))
reg_mort %>% 
  group_by(Year, Occurrence.County) %>% 
  summarise(Total = sum(Deaths, na.rm = T)) %>% 
  filter(Occurrence.County == "Rock County, WI")
```

Based on the provisional data set organized by years (2018 - 2022) we have a table that shows 47252 deaths in 2018, 47511 in 2019, 55263 in 2020, and 52797 in 2021. 




Conclusion 

[ Describe the results of the modeling and analysis section in plain easy to understand language. Determine; are the results significant? How do you know? Why does it matter? ]  

 

Discussion 

[ How might these results impact the audience? Are there any ways in which you could improve the process in future studies? Why should we continue/not continue this kind of study? ] 

 

Sources 

[ Cite any sources that are not your own and when applicable ]  